%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/dogukaankilicarslan}{\Large Dogukaan Kilicarslan}} & Email: \href{mailto:dogukaankilicarslan@gmail.com}{dogukaankilicarslan@gmail.com}\\
  \href{https://github.com/dogukaankilicarslan}{github.com/dogukaankilicarslan} & Mobile: \href{tel:+905326269925}{+90-532-626-9925} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MigrosOne}{Remote}
      {iOS Developer}{December 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Migration Project}
          {Migrated 1.4M-LOC codebase from CocoaPods to Swift Package Manager in 6 weeks, cutting clean-build time 40\% and eliminating workspace merge conflicts.}
        \resumeItem{Architecture Refactoring}
          {Refactored checkout flow into 10 independent MVVM modules, enabling parallel development by 3 developers and reducing PR cycle time 30\%.}
        \resumeItem{Performance Optimization}
          {Optimized UIKit rendering hotspots, holding daily crashes below 0.1\% for 880K DAU and sustaining a 4.8 App Store rating.}
        \resumeItem{CI/CD Pipeline}
          {Set up Xcode Cloud + Bitrise pipelines, trimming test build times from 1-2 days to 2 hours.}
      \resumeItemListEnd

    \resumeSubheading
      {Hepsiburada}{Remote}
      {iOS Developer}{September 2021 -- December 2023}
      \resumeItemListStart
        \resumeItem{User Growth}
          {Doubled active users in 12 months by shipping 20+ features on a seller-facing super-app; lifted rating from 2.3 to 4.7.}
        \resumeItem{Code Quality}
          {Re-engineered legacy screens to VIPER, cutting crash-free sessions from 98.5\% to 99.7\%.}
        \resumeItem{Development Tooling}
          {Authored Bash scripts that generate module templates and enforce coding standard.}
        \resumeItem{Performance Profiling}
          {Led performance profiling with Instruments; resolved two critical memory leaks, reducing app RAM footprint 50\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance}{Remote}
      {Lead iOS Engineer}{February 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Architecture Design}
          {Architecting a SwiftUI product with The Composable Architecture (TCA); manage 3 devs, institute code-owners \& automated linting, achieving crash-free sessions of 99.8\%.}
        \resumeItem{Developer Experience}
          {Built custom CLI tooling to scaffold features and enforce layered new modules, shaving onboarding time for new contributors by 80\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bogazici University}{Istanbul, Turkey}
      {Master of Science in Software Engineering}{2025 -- Current}
    \resumeSubheading
      {Atilim University}{Ankara, Turkey}
      {Bachelor of Science in Avionics Maintenance Engineering}{}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Swift Buddies Community for iOS Developers}
      {Founded and grew an in-person iOS community, hosting relaxed meetups where developers of all levels share knowledge, network, and collaborate. (August 2021 -- Present)}
    \resumeSubItem{iOS Developers Community App}
      {Spearheaded a community-driven app that serves as a hub for developer networking, resources, and events, iterating features based on user feedback. (February 2024 -- Present)}
    \resumeSubItem{AWS/DevOps \& Go Development Bootcamp Assistant}
      {Collaborate with the teacher during the class and take absence of students. Record and upload the session. Evaluate the homework and personally mentor every student. (April 2022 -- September 2022)}
    \resumeSubItem{Blah Blah English Speaking Club}
      {Co-founded and hosted weekly online sessions for non-native English speakers, co-selecting topics and moderating to keep everyone engaged. (July 2020 -- Present)}
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Swift, Python, Bash}
      \hfill
      \textbf{Frameworks}{: SwiftUI, UIKit, RxSwift, Combine, TCA}
    }
    \item{
      \textbf{Architecture}{: MVVM, VIPER, TCA, SOLID Principles, Design Patterns}
      \hfill
      \textbf{Tools}{: Xcode, Instruments, Git, CI/CD}
    }
    \item{
      \textbf{Spoken Languages}{: English (C1), Turkish (Native)}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}